### 2020-03-04 Common/chapters/abstract.tex
Julien and Johan: work repartition + minors

Automating the detection of cancer participates to an an early detection and treatment, which increases the chances of recovery. Recent algorithms in artificial intelligence relying on deep learning have shown promising results in this field. Indeed, the usefulness of convolutional neural networks (CNNs) for segmentation or classification tasks is no longer to be proven. However, the performance of these models is often limited by the amount of available data to train the algorithm.\\
This thesis first presents a state-of-the-art convolutional neural network for prostate lesion classification. All steps from the data processing to the smallest details regarding the neural network training are explained, ensuring a complete reproducibility of the experiment. This model was evaluated on the official SPIE-AAPM-NCI Prostate MR Classification Challenge dataset and achieved an AUC of 0.76. This result constitutes a solid baseline and confirms the correct functioning of our implementation.\\
On top of this implementation, a new transfer learning approach using lesions of multiple body parts (brain and lung) was built. This method shows that integrating information from diverse datasets improves automated prostate cancer diagnosis. Indeed, it appears that lesions of these different types of cancer share low-level features that can be used to increase the generalization ability and performance of the prostate lesion classifier. This technique provides a concrete solution to the lack of available data for prostate classification and suggests that many other types of cancer can take advantage of it.

>>>>

Automating the detection of cancer participates to an an early detection and treatment, which increases the chances of recovery. Recent algorithms in artificial intelligence relying on deep learning have shown promising results in this field. Indeed, the usefulness of convolutional neural networks (CNNs) for segmentation or classification tasks is no longer to be proven. However, the performance of these models is often limited by the amount of available data to train the algorithm.\\
This thesis first presents a state-of-the-art convolutional neural network for prostate lesion classification. All steps from the data processing to the smallest details regarding the neural network training are explained, ensuring a complete reproducibility of the experiment. This model was evaluated on the official SPIE-AAPM-NCI Prostate MR Classification Challenge dataset and achieved an AUC of 0.76. This result constitutes a solid baseline and confirms the correct functioning of the implementation.\\
On top of this implementation, a new transfer learning approach using lesions of multiple body parts (brain and lung) was built. This method shows that integrating information from diverse datasets improves automated prostate cancer diagnosis. Indeed, it appears that lesions of these different types of cancer share low-level features that can be used to increase the generalization ability and performance of the prostate lesion classifier. This technique provides a concrete solution to the lack of available data for prostate classification and suggests that many other types of cancers can take advantage of it.

### 2020-03-04 Common/chapters/acknowledgements.tex
Julien and Johan: work repartition + minors

\textbf{Common acknowledgements:}\\
First of all, we would like to thank Giuseppe Cuccu, for his valuable advices, the exciting discussions we had with him and all the time he took to supervise the project. Even when the results were not there and we were struggling to find the cause, he always encouraged us and pushed us to give our best. We are extremely grateful to him. We also would like to greatly thank Akansha Bhardwaj for her supervision throughout the project and the amazing work she did reviewing the thesis. Last but not least, we would like to express sincere thanks to Philippe Cudré-Mauroux for having supervised the project. Having the opportunity to work with such a team and having access to amazingly powerful machines was literally awesome.\\

>>>>

\textbf{Common acknowledgements:}\\
First of all, we would like to thank Dr. Giuseppe Cuccu for his valuable advices, the exciting discussions we had with him and the precious time he took to supervise the project. Even we were struggling to find the cause of bad results for weeks, he always encouraged us and pushed us to give our best. We are extremely grateful to him for his support. We would also like to greatly thank Akansha Bhardwaj for her supervision throughout the project and the amazing work she did reviewing the thesis. Last but not least, we would like to express sincere thanks to Prof. Dr. Philippe Cudré-Mauroux for supervising the project. Having the opportunity to work with such a wonderful team and having access to amazingly powerful machines was incredible.\\

### 2020-03-04 Common/chapters/introduction.tex
Julien and Johan: work repartition + minors

>>>>

\section{Work repartition}
This thesis was jointly written by two authors. The name(s) of the contributor(s) in the margins of the following chapters only concern the written thesis. Both of them contributed equally to the work leading to the writing of the latter. The work was either done together or in parallel, depending on the tasks. In any case, parts written by one of the authors were reread by the other. Finally, the order in which the names are cited does not represent the quantity of work performed and was chosen arbitrarily.
